---
title: "p8105_hw3_yl4606"
author: "Yubei Liang"
date: "10/9/2020"
output: github_document
---

```{r include=FALSE}
library(tidyverse)
library(p8105.datasets)
knitr::opts_chunk$set(
	fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


### Problem 1

```{r}
data("instacart")
```

This dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns. 

Observations are the level of items in orders by user. There are user / order variables -- user ID, order ID, order day, and order hour. There are also item variables -- name, aisle, department, and some numeric codes. 

1. How many aisles, and which are most items from?

```{r}
instacart %>% 
	count(aisle) %>% 
	arrange(desc(n))
```
There are 134 aisles and fresh vegetables are the one most items from.

2. Let's make a plot

```{r}
instacart %>% 
	count(aisle) %>% 
	filter(n > 10000) %>% 
	mutate(
		aisle = factor(aisle),
		aisle = fct_reorder(aisle, n)
	) %>% 
	ggplot(aes(x = aisle, y = n)) + 
	geom_point() + 
	theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


3. Let's make a table!!

```{r}
instacart %>% 
	filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
	group_by(aisle) %>% 
	count(product_name) %>% 
	mutate(rank = min_rank(desc(n))) %>% 
	filter(rank < 4) %>% 
	arrange(aisle, rank) %>% 
	knitr::kable()
```


4. Apples vs ice cream..

```{r}
instacart %>% 
	filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
	group_by(product_name, order_dow) %>% 
	summarize(mean_hour = mean(order_hour_of_day)) %>% 
	pivot_wider(
		names_from = order_dow,
		values_from = mean_hour
	)
```

### Porblem 2

Load and tidy the data.
```{r message=FALSE}
accelerometer_df = 
  read_csv(
    "./Data/accel_data.csv"
    ) %>% 
  janitor::clean_names()

accelerometer_df =
  accelerometer_df %>% 
      pivot_longer(
        activity_1:activity_1440,
        names_to = "minute",
        values_to = "activity"
      ) %>%
    separate(minute, into = c("act", "minute"), sep = 9) %>%
    mutate(
      day = as.factor(day),
      day = fct_relevel(day, c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")),
      weekday_vs_weekend = recode(day,
        "Monday" = "weekday",
        "Tueday" = "weekday",
        "Wednesday" = "weekday",
        "Thursday" = "weekday",
        "Friday" = "weekday",
        "Saturday" = "weekend",
        "Sunday" = "weekend"
      ))%>%
    group_by(day_id) %>% 
    arrange(day) %>% 
    relocate(week, day, weekday_vs_weekend) %>% 
    select(-c(act, day_id))

accelerometer_df
```

The existing variables include `r names(accelerometer_df)`, and the size of dataset is `r nrow(accelerometer_df)` rows by `r ncol(accelerometer_df)` columns. Therefore, there are `r nrow(accelerometer_df)` observations.
